Fourmile Calibrations

### 2023-02-14 calibration_output.Rmd
everything done on the list except adding relative maps

---
title: "Fourmile Calibrations"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

@@

@@

@@

tm_shape(hrus_map_tmean) +
  tm_polygons('tmean_avg_cumdiff') +
tm_shape(locations) +
  tm_symbols(col='blue', size=4)

@@

tm_shape(hrus_map_precip) +
  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu') +
tm_shape(locations) +
  tm_symbols(col='blue', size=4)

@@

tm_shape(hrus_map_solrad) +
  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd') +
tm_shape(locations) +
  tm_symbols(col='blue', size=4)

>>>>

---
title: "Fourmile Calibrations"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

@@

bouldcr3 <- bouldcr %>%
  mutate(month = month(date)) %>%
  filter(month == 3, year == 2011)

test1 <- ensem_pivot %>%
  mutate(month = month(date)) %>%
  filter(year == 2011,
         month == 3) %>% 
  ggplot(aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs'='black',
                                            "grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
  geom_line(data = bouldcr3, aes(date, bouldcr/10), color = 'darkgrey') +
  scale_y_continuous(name = 'Q_m3s',
                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
  theme_bw() +
  ggtitle('March 2011')

ggplotly(test1) %>%
  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2", 
              inherit=FALSE, showlegend = FALSE) %>%
  layout(yaxis2 = list(overlaying = "y", side = "right",
                       color = 'darkgray',
                       title = "BoulderCr_cms"),
         legend = list(x = 1.1, y = 0.95))

################################################

bouldcr3_2 <- bouldcr %>%
  mutate(month = month(date)) %>%
  filter(month == 3, year == 2019)

test2 <- ensem_pivot %>%
  mutate(month = month(date)) %>%
  filter(year == 2019,
         month == 3) %>% 
  ggplot(aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs'='black',
                                            "grid_ensemble"="maroon", 
                                            "statn_ensemble"="darkturquoise", 
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4', 
                                            "all_ensemble" = "orange")) +
  geom_line(data = bouldcr3_2, aes(date, bouldcr/10), color = 'darkgrey') +
  scale_y_continuous(name = 'Q_m3s',
                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
  theme_bw() +
  ggtitle('March 2019')

ggplotly(test2) %>%
  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2", 
              inherit=FALSE, showlegend = FALSE) %>%
  layout(yaxis2 = list(overlaying = "y", side = "right",
                       color = 'darkgray',
                       title = "BoulderCr_cms"),
         legend = list(x = 1.1, y = 0.95))

@@

```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}

##################
# all 4 with facets

ggplot(gw, aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
  ggtitle('Cumulative RD and RG') +
  theme(text = element_text(size = 24))

@@

locations_t <- locations %>% 
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel',
                        'University Camp SNTL'))

tm_shape(hrus_map_tmean) +
  tm_polygons('tmean_avg_cumdiff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

locations_p <- locations %>%
  filter(type == 'precip')

tm_shape(hrus_map_precip) +
  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
tm_shape(locations_p) +
  tm_symbols(col='blue', size=4)

@@

locations_solrad <- locations %>% 
  dplyr::filter(name %in% c('Gordon_South',
                        'Betasso', 'Niwot_Snotel'))

tm_shape(hrus_map_solrad) +
  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
tm_shape(locations_solrad) +
  tm_symbols(col='blue', size=4)

## Cumulative RH difference

```{r rh, echo = F}

#get rid of a bunch of data
hru_grid_rh <- hru_grids %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_grid = rhum)

hru_statn_rh <- hru_statn %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_statn = rhum)

rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('time', 'ID')) %>%
  mutate(diff = rh_statn - rh_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>% 
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(rh_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')

locations_rh <- locations %>% 
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel'))

tm_shape(hrus_map_rh) +
  tm_polygons('rh_avg_cumdiff', midpoint = NA, id = 'value') +
tm_shape(locations_rh) +
  tm_symbols(col='blue', size=4)

## Cumulative wind difference

```{r wind, echo = F}

#get rid of a bunch of data
hru_grid_wind <- hru_grids %>%
  dplyr::select(c(time, ID, wind)) %>%
  rename(wind_grid = wind)

hru_statn_wind <- hru_statn %>%
  dplyr::select(c(time, ID, wind)) %>%
  rename(wind_statn = wind)

wind_hrus <- left_join(hru_grid_wind, hru_statn_wind, by = c('time', 'ID')) %>%
  mutate(diff = wind_statn - wind_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>% 
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(wind_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_wind <- left_join(hrus, wind_hrus, by = 'value')

locations_w <- locations %>% 
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel'))

tm_shape(hrus_map_wind) +
  tm_polygons('wind_avg_cumdiff', midpoint = NA, id = 'value') +
tm_shape(locations_w) +
  tm_symbols(col='blue', size=4)
